Design, Implementation, and Evaluation of Open Power Quality

### 2020-05-22 02-intro.tex
update structure.

The next sections present an overview of the OPQ system architecture and information architecture. The following section presents related research and technology.  Section \ref{sec:makai} provides more detail on the OPQ Box, and Section \ref{sec:makai} provides more detail on our cloud services. Section \ref{sec:pilot} discusses the pilot deployment of a sensor network and its results. We conclude in Section \ref{sec:conclusion} with some proposals for future research.

>>>>

Section \ref{sec:architecture} presents an overview of the OPQ system architecture and information architecture. Section \ref{sec:related-work} presents related research and technology.  Section \ref{sec:opq-makai} discusses OPQ Box and its triggering system, and Section \ref{sec:opq-makai} discusses our cloud-based analysis services. Section \ref{sec:pilot} discusses the pilot deployment of a sensor network and its results. Section \ref{sec:conclusions} concludes with some proposals for future research.
